\begin{hcarentry}[updated]{Haskell support for the Eclipse IDE}
\label{eclipsefp}
\report{Leif Frenzel}
\status{working, though alpha}
\entry{updated}
\makeheader

The Eclipse platform is an extremely extensible framework for IDEs, developed 
by an Open Source Project. Our project extends it with tools to support Haskell
development.

The aim is to develop an IDE for Haskell that provides the set of features and
the user experience known from the Eclipse Java IDE (the flagship of the 
Eclipse project), and integrates a broad range of Haskell development tools. 
Long-term goals include support for language-aware IDE features, like 
refactoring and structural search.

The current version is 0.10. The project is maintained by Thiago Arrais.

A new subproject, called Cohatoe - 'Contributing Haskell (code) to Eclipse' - 
has developed a framework that allows to partially implement Eclipse Plugins
in Haskell. Building on this framework, an EclipseFP 2 branch has been opened
where EclipseFP functionality is gradually re-implemented in Haskell, and new
functionality is added that integrates existing Haskell tools. Milestone 
builds from the EclipseFP 2 branch are available for download (the latest 
milestone version is 1.102). The Cohatoe subproject and the EclipseFP 2 
branch are maintained by Leif Frenzel.

Every help is very welcome, be it in the form of code contributions, docs or 
tutorials, or just any feedback if you use the IDE. If you want to 
participate, please subscribe to the development mailing list (see below).

\FurtherReading
\begin{compactitem}
\item \url{http://eclipse.org}
\item \url{http://lists.sourceforge.net/lists/listinfo/eclipsefp-develop}
\item Project homepage: \url{http://eclipsefp.sf.net}
\end{compactitem}
\end{hcarentry}
